---
title: "Rmarkdown example"
author: "Ted Laderas"
date: "January 14, 2016"
output: html_document
---

This is an example Rmarkdown report. Open this file up in RStudio and try using different versions of the "Knit" command in the tool bar. 

The first thing to note is that the workspace for the Rmarkdown document starts completely empty. Rmarkdown's workspace is not your current workspace.

```{r}
data(iris)
#produce an xy plot of the iris data
plot(x=iris$Sepal.Width, y=iris$Sepal.Length,col=iris$Species)

#save species to a new varaible
Spec <- iris$Species
```

Note that objects that you create in one codeblock persist to the next:

```{r}
table(Spec)
```

Here's an example of displaying tables. You can import the the knitr library and use the kable function to make your tables look prettier.

```{r}
#standard formatting of table
iris[1:10,]
```

```{r}
library(knitr)
#kable formatting
kable(iris[1:10,])
```

You can even put in-line code in your report. For example, I can say there are `r nrow(iris)` rows in the Iris dataset. This is great in you can regenerate a report if the underlying data has changed, or you reprocess it.

Here's an example of an equation using LaTeX:

$$ \frac{1}{n} \sum_{i=1}^{n} x_{i} $$